Does It Scale? Symbolic Execution of PHP Web Applications

### 2017-01-23 paper.tex
(a)spell checked

\documentclass[sigconf]{acmart}

@@

With respect to the staged nature of web applications it is
non-trivialstatically to determine whether a string literal is an output
candidate, so we heuristically classify string literals as output candidates if
they contain the characters \tt{<}, \tt{>}, or both since we expect output to
contain HTML tags.

@@

% RESULT DIAGRAMS
\begin{figure}[h!]
	\begin{subfigure}[center]{0.48\textwidth}
		\input{new_diagrams/not_reached}
		\caption{
		Classification distribution of \emph{reached} output candidates
		(Reached/Output, OnlyReached) and \emph{not-reached} output candidates
		(FunctionContext, NotImported, Misc) during the analyis for each system.
		\label{coverage}}
	\end{subfigure}
	\vspace{1mm}

@@

\subsubsection{(Dynamic) Includes}
\label{WhyDidIncludesFail}
From Section \ref{sec:experiment_dynamicfeatures} we learn that include
expressions containic symbolic valuescannot be resolution precisely, and from
the previous Section \ref{WhatLiteralsDidWeMiss?} that very little of missed
output candidates can be explained by simply missing to include a file. To
better understand the impact of include expression resolution throughout
analyzing systems, we construct two additional metrics.

@@

Second, we measure how many reached include expressions are
succesfully resolved throughout the analysis for each system.

@@

Aside from being limited by dynamic features, we exercised replacing dynamic
features with respective static counterparts in order to bypass limitations by
manually providing expressions that can be resolved precisely.To use
approaches incorporating symbolic execution with dynamic web applications in
the long run, more concrete input, similar to test oracles, needs
to be provided to decrease the number of assumed symbolic inputs and avoid
dynamic features being confronted with symbolic values. Exising work approaching
this goal \cite{artzi_finding_2008,artzi_finding_2010,DynamicWassermann}
incorporates dynamic symbolic execution, i.e. concrete execution alongside symbolic execution.

@@

Another approach is proposed by Wang et al. \cite{wang_automating_2012}, where
output for a web application is approximated using a hybrid approach: A
dynamic webpage is executed with concrete input and the execution is
recorded at run-time. Changes in the client-side output then can be mapped to 
corresponding PHP code using static impact analysis.

@@

\section{Conclusion}
In this paper we have addressed symbolic execution of PHP web applications that
is used for client page output approximation. These approximations are leveraged
be several developer tools for PHP that yet have not been evaluated for larger
systems. We re-implemented and extended an existing symbolic execution engine
to analyze several real-world PHP applications with the intention to evaluate
the scalability of symbolic execution for PHP. Our work illustrates the
necessity of more comprehensive evaluation of developer tools as
symbolic execution is a conceptually suitable, but not neccessary practical
approach to approximate client page output. Dynamic features of PHP in
combination with symbolic values though can hinder precise symbolic execution
and limit the scalability and practicality of tools relying on symbolically
approximated output.

>>>>

\documentclass[sigconf, preprint]{acmart}

@@

With respect to the staged nature of web applications it is
not trivial to statically determine whether a string literal is an output
candidate. Consequently, we heuristically classify string literals as output
candidates if they contain the characters \tt{<}, \tt{>}, or both since we expect output to
contain HTML tags.

@@

% RESULT DIAGRAMS
\begin{figure}[h!]
	\begin{subfigure}[center]{0.48\textwidth}
		\input{new_diagrams/not_reached}
		\caption{
		Classification distribution of \emph{reached} output candidates
		(Reached/Output, OnlyReached) and \emph{not-reached} output candidates
		(FunctionContext, NotImported, Misc) during the analysis for each system.
		\label{coverage}}
	\end{subfigure}
	\vspace{1mm}

@@

\subsubsection{(Dynamic) Includes}
\label{WhyDidIncludesFail}
From Section \ref{sec:experiment_dynamicfeatures} we learn that include
expressions containing symbolic values cannot be resolution precisely, and from
the previous Section \ref{WhatLiteralsDidWeMiss?} that very little of missed
output candidates can be explained by simply missing to include a file. To
better understand the impact of include expression resolution throughout
analyzing systems, we construct two additional metrics.

@@

Second, we measure how many reached include expressions are
successfully resolved throughout the analysis for each system.

@@

Aside from being limited by dynamic features, we exercised replacing dynamic
features with respective static counterparts in order to bypass limitations by
manually providing expressions that can be resolved precisely.To use
approaches incorporating symbolic execution with dynamic web applications in
the long run, more concrete input, similar to test oracles, needs
to be provided to decrease the number of assumed symbolic inputs and avoid
dynamic features being confronted with symbolic values. Existing work approaching
this goal \cite{artzi_finding_2008,artzi_finding_2010,DynamicWassermann}
incorporates dynamic symbolic execution, i.e. concrete execution alongside symbolic execution.

@@

Another approach is proposed by Wang et al. \cite{wang_automating_2012}, where
output for a web application is approximated using a hybrid approach: A
dynamic web page is executed with concrete input and the execution is
recorded at run-time. Changes in the client-side output then can be mapped to 
corresponding PHP code using static impact analysis.

@@

\section{Conclusion}
In this paper we have addressed symbolic execution of PHP web applications that
is used for client page output approximation. These approximations are leveraged
be several developer tools for PHP that yet have not been evaluated for larger
systems. We re-implemented and extended an existing symbolic execution engine
to analyze several real-world PHP applications with the intention to evaluate
the scalability of symbolic execution for PHP. Our work illustrates the
necessity of more comprehensive evaluation of developer tools as
symbolic execution is a conceptually suitable, but not necessary practical
approach to approximate client page output. Dynamic features of PHP in
combination with symbolic values though can hinder precise symbolic execution
and limit the scalability and practicality of tools relying on symbolically
approximated output.
